Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-12-15 prop_letter_ajhs.tex
prop_letter_ajhs.tex Add citations...

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical IVPMs. The proof of
this fact is included in the forthcoming thesis by the first author. A
consequence of this fact is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.

@@

The proof, detailed in the forthcoming thesis, proceeds as
follows. From a subspace $\eventsC$ of mutually commuting events, one
can construct a partial orthonormal basis by diagonalization, and
complete this to a full orthonormal basis $\overline{\eventsC}$.  We
can then build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis.  Using this correspondence together with
the classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core.

>>>>

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting events,
$\eventsC$, recovers the definition of classical
IVPMs~\cite{JamisonLodwick2004}. The proof of this fact is included in the
forthcoming thesis by the first author~\citep{TaiThesis2018}. A
consequence of this fact is that known properties of classical IVPMs
directly hold for QIVPMs when one restricts to mutually commuting
events, $\eventsC$. In particular, in the classical world, it is
\emph{impossible} for experiments to result in probabilities that are
inconsistent with \emph{some} state of the system under consideration,
i.e., all IVPMs must have a non-empty ``core''~\footnote{A result by
  Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016}
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}. Interestingly, as we show in
Sec.~\ref{sec:Gleason}, it is possible in the quantum world for the
probabilities associated with some events to be inconsistent with
\emph{any} quantum state, i.e., for the QIVPM to have an empty core;
in that case, one cannot guarantee non-empty cores for finite-precision
attempts at proving Gleason's theorem by extending the Born measure
$\muB_{\rho}\left(P\right)$ to QIVPMs
$\bar{\mu}\left(P\right)$. However, if the set of events is mutually
commuting, the situation reverts to the classical case in which
probabilities always determine at least one state.

@@

The proof, detailed in the forthcoming thesis~\citep{TaiThesis2018}, proceeds as
follows. From a subspace $\eventsC$ of mutually commuting events, one
can construct a partial orthonormal basis by diagonalization, and
complete this to a full orthonormal basis $\overline{\eventsC}$.  We
can then build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis.  Using this correspondence together with
the classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core.
